Examining the Multifaceted Impact of Family Size on Happiness, Health, Gender Dynamics, and Financial Well-being

### 2023-04-05 outputs/paper/paper.qmd
Add files via upload

This research investigates the diverse effects of family size on various aspects such as happiness, health, gender roles, and financial stability. The study employs cross-sectional cumulative microdata from the United States spanning from 1972 to 2012.The impact of the number of children in a family on various aspects of family life has been a topic of interest for researchers and policymakers alike [@a]. Family size and structure play a crucial role in shaping the lives of individuals and communities. Understanding the connections between the number of children and factors such as happiness, health, sex distribution, and financial satisfaction can help inform decisions and policies aimed at promoting family well being [@b]. This paper seeks to explore these relationships and shed light on the complex interplay between family size and various aspects of family life.

@@

```{r}
#| echo: false
#| warning: false
data %>%
  select(6:10) %>%
  slice(1:5) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

>>>>

This research investigates the diverse effects of family size on various aspects such as happiness, health, gender roles, and financial stability. The study employs cross-sectional cumulative micro data from the United States spanning from 1972 to 2012.The impact of the number of children in a family on various aspects of family life has been a topic of interest for researchers and policymakers alike [@a]. Family size and structure play a crucial role in shaping the lives of individuals and communities. Understanding the connections between the number of children and factors such as happiness, health, sex distribution, and financial satisfaction can help inform decisions and policies aimed at promoting family well being [@b]. This paper seeks to explore these relationships and shed light on the complex interplay between family size and various aspects of family life.

@@

```{r}
#| echo: false
#| warning: false
data %>%
  select(7:10) %>%
  slice(1:5) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```
